%-------------------------
% Resume in Latex
% Author : Jake Gutierrez (Base Template)
% Adapted by: Gemini
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Muhmmad Sheheryar Raza} \\ \vspace{1pt}
    \small 923066105428 $|$ \href{mailto:m.sheheryarraza@gmail.com}{\underline{m.sheheryarraza@gmail.com}} $|$
    \href{https://linkedin.com/in/muhammad-sheheryar-raza}{\underline{linkedin/muhammad-sheheryar-raza}} $|$
    \href{https://github.com/SheheryarRaza}{\underline{github.com/SheheryarRaza}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
  \resumeSubHeadingListStart
    \resumeItem{Results-driven .NET Developer with expertise in C/#, ASP.NET Core, Entity Framework Core, and SQL Server. Experienced in building RESTful APIs and delivering end-to-end web solutions. Proven success through projects like an e-commerce platform, an IGNITE-funded IoT smart home system, and a cross-device clipboard synchronization platform.}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Gift University}{2020 -- 2024}
      {BS Computer Science}{}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Data Structures and Algorithms, Database Management Systems, Software Engineering, Web Development}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {.NET Core Developer}{Oct 2024 -- Jul 2025}
      {Eratech}{}
      \resumeItemListStart
        \resumeItem{Developed backend modules for both web and desktop applications using ASP.NET Core and C\#.}
        \resumeItem{Built and maintained APIs with Entity Framework Core and SQL Server; implemented JWT-based authentication and secure session handling.}
        \resumeItem{Contributed to POS system features, worked on WPF UI integration, and gained practical experience on production-level backend architecture.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{CopyHere – Cross-Device Clipboard Synchronization Platform} $|$ \emph{}}{Jul 2025 -- Aug 2025}
          \resumeItemListStart
            \resumeItem{Designed and developed the entire backend architecture using ASP.NET Core 8.0 with Clean Architecture principles.}
            \resumeItem{SignalR for real-time communication, Entity Framework Core, SQL Server, JWT authentication, and Vanilla JavaScript frontend.}
            \resumeItem{Real-time clipboard sync across devices, clipboard history with search and filtering, device management, tagging, and rate limiting.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Task Management API} $|$ \emph{}}{Jun 2025 -- Jul 2025}
          \resumeItemListStart
            \resumeItem{Sole developer responsible for designing API structure, implementing authentication, and building core features.}
            \resumeItem{ASP.NET Core, Entity Framework Core, SQL Server, JWT, Role-based Authorization.}
            \resumeItem{Task/subtask management with soft deletion, prioritization, tagging, background notifications, centralized error handling, and structured logging.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{E-Commerce Web Application} $|$ \emph{}}{Feb 2025 -- Mar 2025}
          \resumeItemListStart
            \resumeItem{Full-stack developer handling backend logic, database design, and API creation.}
            \resumeItem{ ASP.NET Core, Entity Framework Core, .NET Identity, MVC Architecture, SQL Server.}
            \resumeItem{Secure authentication, product catalog, order processing modules, and RESTful APIs}
          \resumeItemListEnd




%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages}{: C\#, Python, Angular (Basic)} \\
      \textbf{Frameworks/ Libraries}{: ASP.NET Core, .NET Core, Entity Framework Core, .NET Identity, WPF, Ajax} \\
      \textbf{Web Technologies}{: RESTful APIs, JWT Authentication, MVC, LINQ, Clean Architecture} \\
      \textbf{Databases}{: SQL Server} \\
      \textbf{Tools / Platforms}{: Visual Studio, Git, Swagger, Postman} \\
    }}
  \end{itemize}

% The Certifications and Awards sections are not present in the provided template, so they are omitted.

%-------------------------------------------
\end{document}
